\textbf{\hmwkTitle} \\ \smallskip \normalsize{\hmwkSubtitle} \\ \hmwkClass \\ \normalsize{\hmwkClassInstructor} \\

### 2017-05-19 paper/main.tex
tweaked report slightly

Our project aims to explore this view by implementing a simple physics engine
in scheme. We designed the physics engine to be generic and extensible. For
example, it is very straightforward to define new worlds on the underlying
substrate as well as to define new objects and forces within a given world.
This paper presents the design of the infrastructure for the physics engine,
describes how objects and forces can be easily defined and added on top of the
infrastucture, and illustrate several demonstrations of the system on worlds
with gravitational and electrostatic forces.

@@

Our system adopted the second model where each object updates itself. This
model makes it easier to handle different types of forces exerted on specific
types of object. Moreover, in the second model, the engine does not need to be
notified and updated everytime a new object is added. Instead, update or
addition of new \texttt{interaction}s is taken care of at the object level when
it is added.

@@

>>>>

Our project aims to explore this view by implementing a simple physics engine
in scheme. We designed the physics engine to be generic and extensible. For
example, it is very straightforward to define new worlds on the underlying
substrate as well as to define new objects and forces within a given world. We
attempt to impose as little constraint on the behavior of the objects as
possible, by allowing them to control how they are updated over time.  This
paper presents the design of the infrastructure for the physics engine,
describes how objects and forces can be easily defined and added on top of the
infrastucture, and illustrate several demonstrations of the system on worlds
with gravitational and electrostatic forces.

All code for this project can be viewed at
\texttt{https://github.com/mbchang/6.945-physics}.

@@

Our system adopted the second model where each object updates itself. This
model makes it easier to handle different types of forces exerted on specific
types of object. Moreover, in the second model, the engine does not need to be
notified and updated every time a new object is added. Instead, update or
addition of new \texttt{interaction}s is taken care of at the object level when
it is added.

@@

Seeing as objects can choose how to update themselves, objects which behave in
exotic ways, not necessarily obeying any physical laws or principles, could be
added and integrated with physical objects.
